title: 
author: "Scott Deming"

##3. Open a new R Markdown file and save it to the repository with the filename `formative.rmd`. Inlcude all your code in the markdown document.

##4. Upload the MITx/Harvardx dataset to R as a dataframe named `D1`(Please inlcude your code in your markdown document)

#5. What does the `DI` suffix that is appeneded to two (five) of the variable names mean?
`DI` suffix may mean `Descrete Identifier` for a suffix tree. 

6. How many people enrolled in HarvardX/CS50x recieved certification in 2012? (Please inlcude your code in your markdown document) `187,308` 
7. How many people registered for HarvardX/CS50x from Columbia on October 15, 2012? (Please inlcude your code in your markdown document)

8. Create a new data frame (`D2`) that includes student ID and registration date for all students from a country of your choice (Please inlcude your code in your markdown document)

9. Create a new data frame (`D3`) in which the column names are the registration dates, with one column containing the student ids and all other cells indicating a `1` if the student registered on that date or an `NA` if they did not (hint: you will need to create a new variable before you change the structure of your data frame)

10. Now make the row names of `D3` the student ids on your new data frame and remove the user id column from your data frame

11. Convert your data frame to a matrix (`M1`)

12. Create a new matrix which is the transposed version of your matrix (`M2`)

13. Create a third matrix (`M3`) that is a student by student matrix where the cells in the matrix represent if two studentes registered on the same day (This will take a lot of processing power, you may not be able to complete it if you have a large number of students)

14. Convert the diagonal of your matrix into `NA`s
```{r}
D1 <- as.data.frame(HMXPC13_DI_v2_5_14_14)
```


```{r}
group_by(D1, course_id, certified ) 
```
#`6`#
```{r}
sum(D1$course_id=="HarvardX/CS50x/2012", D1$certified==1)
```
#`7`#
```{r}
sum(D1$course_id=="HarvardX/CS50x/2012", D1$registered==1, D1$final_cc_cname_DI=="Colombia", D1$userid_DI, D1$start_time_DI==10/15/2012)
```
#`8`#
```{r}
D1_UAE <- filter(D1, final_cc_cname_DI=="UAE")
```
# zero UAE



